Contextuality and the Born Rule in Fuzzy Quantum Theories

### 2017-03-14 prop_letter.tex
prop_letter.tex Fix a bug according to https://tex.stackexchange.com/questions/37076/is-it-possible-to-load-biblatex-with-a-class-that-has-already-loaded-natbib/37077#37077
prop_letter.tex Went through "REVTeX 4.1 Author's Guide"

\documentclass[reprint, aps, prl,superscriptaddress, showpacs,
showkeys]{revtex4-1} 
\let\bibhang\relax
\let\citename\relax
\let\bibfont\relax
\let\Citeauthor\relax
\let\textcite\relax
\makeatletter
\DeclareRobustCommand{\MakeUppercase}[1]{{%
      \def\i{I}\def\j{J}%
      \def\reserved@a##1##2{\let##1##2\reserved@a}%
      \expandafter\reserved@a\@uclclist\reserved@b{\reserved@b\@gobble}%
      \protected@edef\reserved@a{\uppercase{#1}}%
      \reserved@a
   }}
\DeclareRobustCommand{\MakeLowercase}[1]{{%
      \def\reserved@a##1##2{\let##2##1\reserved@a}%
      \expandafter\reserved@a\@uclclist\reserved@b{\reserved@b\@gobble}%
      \protected@edef\reserved@a{\lowercase{#1}}%
      \reserved@a
   }}
\makeatother
\expandafter\let\csname ver@natbib.sty\endcsname\relax
\renewcommand{\bibliography}[1]{}
\usepackage[ backend=biber,style=phys]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{hyperref}

@@

\begin{document}

@@

@@

The
Kochen-Specker theorem asserts that there is no function~$v$ assigning
a definitely value to all observables such that
\begin{eqnarray}
v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
\label{eq:Kochen-Specker-Rules}\end{eqnarray}
if $O_{1}$ and $O_{2}$ are commuting observables. Suppose that there
is a function~$v$ satisfying these two properties, it must send
an observable to its eigenvalues so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{array}{ccc}
\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
\end{array}\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a function~$v$ such that
\begin{equation}
\begin{array}{ccc}
v\left(\mathbb{1}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\mathbb{1}\right) & v\left(\sigma_{z}\otimes\sigma_{z}\right)\\
v\left(\sigma_{x}\otimes\mathbb{1}\right) & v\left(\mathbb{1}\otimes\sigma_{x}\right) & v\left(\sigma_{x}\otimes\sigma_{x}\right)\\
v\left(\sigma_{x}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\sigma_{x}\right) & v\left(\sigma_{y}\otimes\sigma_{y}\right)
\end{array}\label{eq:MerminSquare-values}
\end{equation}
satisfying equation~(\ref{eq:Kochen-Specker-Rules}).

\begin{table}

@@

@@

\end{table}

@@

1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 0) + f(0, 0, 0, 1)\textrm{ and}\\
1 = f(-1, 1, 1, 1) + f(1, -1, 1, 1) + f(1, 1, -1, 1) + f(1, 1, 1, -1)

@@

1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 1) + f(0, 0, 1, -1)\textrm{ ,}\\
1 = f(1, 0, 0, 0) + f(0, 0, 1, 0) + f(0, 1, 0, 1) + f(0, 1, 0, -1)\textrm{ ,}\\
1 = f(1, 0, 0, 0) + f(0, 0, 0, 1) + f(0, 1, 1, 0) + f(0, 1, -1, 0)\textrm{ ,}\\
1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(1, 0, 1, 0) + f(0, 1, 0, -1)\textrm{ ,}\\
1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(0, 1, 1, 0) + f(1, 0, 0, -1)\textrm{ ,}\\
1 = f(1, 1, -1, 1) + f(1, 1, 1, -1) + f(0, 0, 1, 1) + f(1, -1, 0, 0)\textrm{ ,}\\
1 = f(0, 1, -1, 0) + f(1, 0, 0, -1) + f(1, 1, 1, 1) + f(1, -1, -1, 1)\textrm{ ,}\\
1 = f(0, 0, 1, -1) + f(1, -1, 0, 0) + f(1, 1, 1, 1) + f(1, 1, -1, -1)\textrm{ ,}\\
1 = f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) + f(1, -1, -1, 1)\textrm{ .}

@@

\begin{example}[Four-dimensional quantum real-valued probability
measure]\label{ex:four-dimensional-real-value}Consider the frame
function~$f:\mathcal{T}_{24}\rightarrow\left[0,1\right]$ again.
Apart from equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2},
$f$ should also satisfy the following equations: 
\begin{eqnarray}
1 = f(0,0,1,0)+f(0,1,0,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
1 = f(0,1,-1,0)+f(0,1,1,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
1 = f(0,0,0,1)+f(0,1,0,0)+f(1,0,-1,0)+f(1,0,1,0)\textrm{ ,}\\ 
1 = f(0,1,0,-1)+f(0,1,0,1)+f(1,0,-1,0)+f(1,0,1,0)\textrm{ ,}\\ 
1 = f(0,1,1,0)+f(1,-1,1,-1)+f(1,0,0,1)+f(1,1,-1,-1)\textrm{ ,}\\ 
1 = f(0,0,0,1)+f(0,0,1,0)+f(1,-1,0,0)+f(1,1,0,0)\textrm{ ,}\\ 
1 = f(0,0,1,-1)+f(0,0,1,1)+f(1,-1,0,0)+f(1,1,0,0)\textrm{ ,}\\ 
1 = f(0,0,1,1)+f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,0,0)\textrm{ ,}\\ 
1 = f(-1,1,1,1)+f(0,0,1,-1)+f(1,-1,1,1)+f(1,1,0,0)\textrm{ ,}\\ 
1 = f(0,1,0,1)+f(1,-1,1,1)+f(1,0,-1,0)+f(1,1,1,-1)\textrm{ ,}\\ 
1 = f(-1,1,1,1)+f(0,1,-1,0)+f(1,0,0,1)+f(1,1,1,-1)\textrm{ ,}\\ 
1 = f(0,1,0,-1)+f(1,-1,1,-1)+f(1,0,-1,0)+f(1,1,1,1)\textrm{ ,}\\ 
1 = f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,-1,-1)+f(1,1,1,1)\textrm{ .} 
\label{eq:non-Kernaghan}\end{eqnarray}
\qed\end{example}

\begin{example}[Four-dimensional quantum three-interval-valued probability
measure]\label{ex:four-dimensional-three-value}Consider the orthonormal
basis~$\left\{ \ket{0},\ket{1},\ket{2},\ket{3}\right\} $ as defined
in table~\ref{table:commonBasis}. Let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$. Then, we can
define a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}_{1}$
as follow. 
\begin{eqnarray}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})=\imposs\textrm{ ,}\\ 
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\textrm{ ,}\\ 
\bar{\mu}(P) = \unknown\qquad\textrm{otherwise.} 
\end{eqnarray}
To verify $\bar{\mu}$ is a quantum IVPM, first notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
by induction. Second, equation (\ref{eq:QuantumInterval-valuedProbability-Complement})
implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
Therefore, to prove equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
it is sufficient to check
\begin{eqnarray}
\bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)\textrm{ ,}\\
\bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}+\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)
\end{eqnarray}
for orthogonal $\ket{\psi_{0}}$, $\ket{\psi_{1}}$, and $\ket{\psi_{2}}$.
This equation always holds because $\unknown$ is a subset of the
left-hand side of both of the equations.

>>>>

\documentclass[reprint, aps, prl,superscriptaddress, showpacs,
showkeys]{revtex4-1} 
% Follow 
% https://tex.stackexchange.com/questions/37076/is-it-possible-to-load-biblatex-with-a-class-that-has-already-loaded-natbib/37077#37077
% to put RevTeX with BibLaTeX
\let\bibhang\relax
\let\citename\relax
\let\bibfont\relax
\let\Citeauthor\relax
\let\textcite\relax
\makeatletter
\DeclareRobustCommand{\MakeUppercase}[1]{{%
      \def\i{I}\def\j{J}%
      \def\reserved@a##1##2{\let##1##2\reserved@a}%
      \expandafter\reserved@a\@uclclist\reserved@b{\reserved@b\@gobble}%
      \protected@edef\reserved@a{\uppercase{#1}}%
      \reserved@a
   }}
\DeclareRobustCommand{\MakeLowercase}[1]{{%
      \def\reserved@a##1##2{\let##2##1\reserved@a}%
      \expandafter\reserved@a\@uclclist\reserved@b{\reserved@b\@gobble}%
      \protected@edef\reserved@a{\lowercase{#1}}%
      \reserved@a
   }}
\makeatother
\expandafter\let\csname ver@natbib.sty\endcsname\relax
\usepackage[ backend=biber,style=phys]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{hyperref}

@@

\begin{document}
\renewcommand{\bibliography}[1]{}

@@

\begin{abstract}
\begin{description}
\item[Background] This paper wants to understand the quantum measurement in the
bounded resource.
\item[Purpose] ?
\item[Method] We replace quantum real-valued probability measures by
interval-valued ones whose range can be restricted to finite number of
intervals representing finite precision measurement.
\item[Results] Quantum interval-valued probability measures provide a unified
framework to interpret the Kochen-Specker theorem and Gleason's theorem. We also
found some legitimate quantum interval-valued probability measures which cannot
be explained by the Born rule.
\item[Conclusions] Our research provide a new insight of the role of finite
precision measurement when formulate quantum theory.
\end{description}
\end{abstract}

@@

The
Kochen-Specker theorem asserts that there is no function~$v$ assigning
a definitely value to all observables such that
\begin{eqnarray}
& & v\left(O_{1}\right)+v\left(O_{2}\right)=v\left(O_{1}+O_{2}\right)\textrm{ and}\\
& & v\left(O_{1}\right)v\left(O_{2}\right)=v\left(O_{1}O_{2}\right)
\label{eq:Kochen-Specker-Rules}\end{eqnarray}
if $O_{1}$ and $O_{2}$ are commuting observables. Suppose that there
is a function~$v$ satisfying these two properties, it must send
an observable to its eigenvalues so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{array}{ccc}
\mathbb{1}\otimes\sigma_{z} & \sigma_{z}\otimes\mathbb{1} & \sigma_{z}\otimes\sigma_{z}\\
\sigma_{x}\otimes\mathbb{1} & \mathbb{1}\otimes\sigma_{x} & \sigma_{x}\otimes\sigma_{x}\\
\sigma_{x}\otimes\sigma_{z} & \sigma_{z}\otimes\sigma_{x} & \sigma_{y}\otimes\sigma_{y}
\end{array}\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a function~$v$ such that
\begin{equation}
\begin{array}{ccc}
v\left(\mathbb{1}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\mathbb{1}\right) & v\left(\sigma_{z}\otimes\sigma_{z}\right)\\
v\left(\sigma_{x}\otimes\mathbb{1}\right) & v\left(\mathbb{1}\otimes\sigma_{x}\right) & v\left(\sigma_{x}\otimes\sigma_{x}\right)\\
v\left(\sigma_{x}\otimes\sigma_{z}\right) & v\left(\sigma_{z}\otimes\sigma_{x}\right) & v\left(\sigma_{y}\otimes\sigma_{y}\right)
\end{array}\label{eq:MerminSquare-values}
\end{equation}
satisfying equation~(\ref{eq:Kochen-Specker-Rules}).

\begin{table*}

@@

\hline

@@

\end{table*}

@@

& & 1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 0) + f(0, 0, 0, 1)\textrm{ and}\\
& & 1 = f(-1, 1, 1, 1) + f(1, -1, 1, 1) + f(1, 1, -1, 1) + f(1, 1, 1, -1)

@@

& & 1 = f(1, 0, 0, 0) + f(0, 1, 0, 0) + f(0, 0, 1, 1) + f(0, 0, 1, -1)\textrm{ ,}\\
& & 1 = f(1, 0, 0, 0) + f(0, 0, 1, 0) + f(0, 1, 0, 1) + f(0, 1, 0, -1)\textrm{ ,}\\
& & 1 = f(1, 0, 0, 0) + f(0, 0, 0, 1) + f(0, 1, 1, 0) + f(0, 1, -1, 0)\textrm{ ,}\\
& & 1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(1, 0, 1, 0) + f(0, 1, 0, -1)\textrm{ ,}\\
& & 1 = f(-1, 1, 1, 1) + f(1, 1, -1, 1) + f(0, 1, 1, 0) + f(1, 0, 0, -1)\textrm{ ,}\\
& & 1 = f(1, 1, -1, 1) + f(1, 1, 1, -1) + f(0, 0, 1, 1) + f(1, -1, 0, 0)\textrm{ ,}\\
& & 1 = f(0, 1, -1, 0) + f(1, 0, 0, -1) + f(1, 1, 1, 1) + f(1, -1, -1, 1)\textrm{ ,}\\
& & 1 = f(0, 0, 1, -1) + f(1, -1, 0, 0) + f(1, 1, 1, 1) + f(1, 1, -1, -1)\textrm{ ,}\\
& & 1 = f(1, 0, 1, 0) + f(0, 1, 0, 1) + f(1, 1, -1, -1) + f(1, -1, -1, 1)\textrm{ .}

@@

\begin{example}[Four-dimensional quantum real-valued probability
measure]\label{ex:four-dimensional-real-value}Consider the frame
function~$f:\mathcal{T}_{24}\rightarrow\left[0,1\right]$ again.
Apart from equation~\ref{eq:Kernaghan-1} and \ref{eq:Kernaghan-2},
$f$ should also satisfy the following equations: 
\begin{eqnarray}
& & 1 = f(0,0,1,0)+f(0,1,0,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
& & 1 = f(0,1,-1,0)+f(0,1,1,0)+f(1,0,0,-1)+f(1,0,0,1)\textrm{ ,}\\ 
& & 1 = f(0,0,0,1)+f(0,1,0,0)+f(1,0,-1,0)+f(1,0,1,0)\textrm{ ,}\\ 
& & 1 = f(0,1,0,-1)+f(0,1,0,1)+f(1,0,-1,0)+f(1,0,1,0)\textrm{ ,}\\ 
& & 1 = f(0,1,1,0)+f(1,-1,1,-1)+f(1,0,0,1)+f(1,1,-1,-1)\textrm{ ,}\\ 
& & 1 = f(0,0,0,1)+f(0,0,1,0)+f(1,-1,0,0)+f(1,1,0,0)\textrm{ ,}\\ 
& & 1 = f(0,0,1,-1)+f(0,0,1,1)+f(1,-1,0,0)+f(1,1,0,0)\textrm{ ,}\\ 
& & 1 = f(0,0,1,1)+f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,0,0)\textrm{ ,}\\ 
& & 1 = f(-1,1,1,1)+f(0,0,1,-1)+f(1,-1,1,1)+f(1,1,0,0)\textrm{ ,}\\ 
& & 1 = f(0,1,0,1)+f(1,-1,1,1)+f(1,0,-1,0)+f(1,1,1,-1)\textrm{ ,}\\ 
& & 1 = f(-1,1,1,1)+f(0,1,-1,0)+f(1,0,0,1)+f(1,1,1,-1)\textrm{ ,}\\ 
& & 1 = f(0,1,0,-1)+f(1,-1,1,-1)+f(1,0,-1,0)+f(1,1,1,1)\textrm{ ,}\\ 
& & 1 = f(1,-1,-1,1)+f(1,-1,1,-1)+f(1,1,-1,-1)+f(1,1,1,1)\textrm{ .} 
\label{eq:non-Kernaghan}\end{eqnarray}
\qed\end{example}

\begin{example}[Four-dimensional quantum three-interval-valued probability
measure]\label{ex:four-dimensional-three-value}Consider the orthonormal
basis~$\left\{ \ket{0},\ket{1},\ket{2},\ket{3}\right\} $ as defined
in table~\ref{table:commonBasis}. Let $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$. Then, we can
define a quantum IVPM~$\bar{\mu}:\events_{24}\rightarrow\mathscr{I}_{1}$
as follow. 
\begin{eqnarray}
& & \bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})=\imposs\textrm{ ,}\\ 
& & \bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})=\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})=\necess\textrm{ ,}\\ 
& & \bar{\mu}(P) = \unknown\qquad\textrm{otherwise.} 
\end{eqnarray}
To verify $\bar{\mu}$ is a quantum IVPM, first notice that $\bar{\mu}\left(P_{0}+P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)$
implies equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion})
by induction. Second, equation (\ref{eq:QuantumInterval-valuedProbability-Complement})
implies $\bar{\mu}\left(\mathbb{1}\right)\subseteq\bar{\mu}\left(P\right)+\bar{\mu}\left(\mathbb{1}-P\right)$.
Therefore, to prove equation (\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
it is sufficient to check
\begin{eqnarray}
& & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}\right)\textrm{ ,}\\
& & \bar{\mu}\left(\proj{\psi_{0}}+\proj{\psi_{1}}+\proj{\psi_{2}}\right)\subseteq\bar{\mu}\left(\proj{\psi_{0}}\right)+\bar{\mu}\left(\proj{\psi_{1}}+\proj{\psi_{2}}\right)
\end{eqnarray}
for orthogonal $\ket{\psi_{0}}$, $\ket{\psi_{1}}$, and $\ket{\psi_{2}}$.
This equation always holds because $\unknown$ is a subset of the
left-hand side of both of the equations.
